Papers

### 2025-09-07 papers.qmd
update

@@

-   Brand, C. O., Brady, D., & Stafford, T. (2023, June 27). [The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://psyarxiv.com/2e9wn). https://doi.org/10.31234/osf.io/2e9wn

@@

- Boag, R. J., Innes, R. J., Stevenson, N., Bahg, G., Busemeyer, J. R., Cox, G. E., … Forstmann, B. (2024, July 2). [An expert guide to planning experimental tasks for evidence accumulation modelling](https://osf.io/preprints/psyarxiv/snqgp).

-   Brand, C. O., Brady, D., & Stafford, T. (2023, June 27). [The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://psyarxiv.com/2e9wn). https://doi.org/10.31234/osf.io/2e9wn

@@

-   Brand, C. O., & Stafford, T. (2022). [Using dialogues to increase positive attitudes towards COVID-19 vaccines in a vaccine-hesitant UK population](https://royalsocietypublishing.org/doi/full/10.1098/rsos.220366). Royal Society Open Science, 9(10), 220366.

>>>>

- Butters, A., Marshall, M. B., Pinfield, S., Stafford, T., Bondarenko, A., Neubauer, B., Nuske, R., Schwidlinski, P., & Denecke, H. (2025). [Applicants as Reviewers: Evaluating the Risks, Benefits, and Potential of Distributed Peer Review for Grant Funding Allocations](https://doi.org/10.6084/m9.figshare.29994841.v2) (RoRI Working Paper No. 17). https://doi.org/10.6084/m9.figshare.29994841.v2

@@

-   Brand, C. O., Brady, D., & Stafford, T. (in press). [The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://psyarxiv.com/2e9wn). *Cognitive Science*. https://doi.org/10.31234/osf.io/2e9wn

@@

@@

-   Brand, C. O., & Stafford, T. (2022). [Using dialogues to increase positive attitudes towards COVID-19 vaccines in a vaccine-hesitant UK population](https://royalsocietypublishing.org/doi/full/10.1098/rsos.220366). Royal Society Open Science, 9(10), 220366. <https://doi.org/10.1098/rsos.220366>
